---
title: "Untitled"
author: "Fermano, Aaron John"
date: "2024-03-07"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("tidyverse")
```
```

#A. Load the built-in warpbreaks dataset.
```{r}
structure(warpbreaks)
```

#A1. Find out, in a single command, which columns of warpbreaks are either numeric or integer. What are the data types of each column?
```{r}
warpbreak <- sapply(warpbreaks, function(x) typeof(x))
warpbreak
```

#A2. How many observations does it have?
```{r}
nrow(warpbreaks)
```

#A3. Is numeric a natural data type for the columns which are stored as such? Convert tointeger when necessary.
```{r}
warpbreaks$breaks <- as.integer(warpbreaks$breaks)
```

#A4. Error messages in R sometimes report the underlying type of an object rather than theuser-level class. Derive from the following code and error message what theunderlying type. Explain what is the error all about. Do not just copy the error message that was displayed.
```{r}
warpbreaks$breaks + 1
```

#B. Load the exampleFile.txt
#B1. Read the complete file using readLines.
```{r}
BexampleFile <- readLines("exampleFile.txt")
print(BexampleFile)
```

#B2. Separate the vector of lines into a vector containing comments and a vector
containing the data. Hint: use grepl.
```{r}
Blines <- strsplit(BexampleFile, "\n")[[1]]

Bcomments <- Blines[grepl("^#", Blines)]
Bdata <- Blines[!grepl("^#", Blines)]
```

#B3. Extract the date from the first comment line and display on the screen “It was created data.”
```{r}
(date <- gsub(".*Created : ", "", Bcomments[1]))
paste0("It was created ", date)
```

#B4. Read the data into a matrix as follows.
#Ba. Split the character vectors in the vector containing data lines by semicolon (;) using strsplit.
